### 2020-01-01 methods.tex
added methods section

Let us write the Energy Landscape (or optimization function) for a typical DNN with $L$ layers, with activation functions $h_{l}(\cdot)$, and with $N\times M$)  weight matrices $\mathbf{W}_{l}$, and the biases $\mathbf{b}_{l}$, as follows:
\begin{equation}
E_{DNN}=h_{L}(\mathbf{W}_{L}\times h_{L-1}(\mathbf{W}_{L-1}\times h_{L-2}(\cdots)+\mathbf{b}_{L-1})+\mathbf{b}_{L})  .
\label{eqn:dnn_energy}
\end{equation}

The model has been (or will be) trained on (unspecified) labeled data $\{d_{i},y_{i}\}\in\mathcal{D}$, 
using Backprop, by minimizing some (also unspecified) loss function $\mathcal{L}()$.  Moreover, we expect that most well trained,. production quality models will employ 1 or more forms of on regularization, such as Batch Normalization, Dropout, etc, and will also contain additional structure such as Skip Connections etc. Here, we ignore these details, and focus only on the weight matrices.  Each layer contains by one or more layer 2D weight matrices $\mathbf{W}_{L}$, and/or the 2D feature maps $\mathbf{W}_{i,L}$ extracted from 2D Convolutional layers.  (For notational convenience, we may drop the $i$ and/or $i,l$ subscripts below.)

We assume the layer weight matrices are statistically independent, allowing us to estimate the Complexity, or test accuracy, with a standard Product Norm, which resembles a data dependent VC complexity

\begin{equation}
\mathcal{C}\sim\Vert\mathbf{W}_{1}\Vert\times\Vert\mathbf{W}_{2}\Vert\cdots\Vert\mathbf{W}_{L}\Vert ,
\end{equation}
where $mathbf{W}$ is an $(N\times M)$ weight matrix, with $N\ge M$, and 
 $\Vert\mathbf{W}\Vert$ is some matrix Norm.

\begin{itemize}
 \item Frobenius Norm: $\Vert\mathbf{W}\Vert^{2}_{F}=\Vert\mathbf{W}\Vert^{2}_{2}=\sum_{i,j}W^{2}_{i,j}$,
 \item Spectral Norm:  $\Vert\mathbf{W}\Vert_{\infty}=\lambda_{max}$, or even the
 \item $\alpha$-Norm (or Shatten Norm) $\Vert\mathbf{W}\Vert^{alpha}_{\alpha}=\sum_{i=1}^{M}\lambda^{\alpha}$,
\end{itemize}

where $\lamba_{i}$ is the i-th eigenvalue of the correlation matrix $\mathbf{X}$

\begin{equation}
\mathbf{X}=\dfrac{1}{N}\mathbf{W}^{T}\mathbf{W},
\end{equation}

$lambda_{max}$ is the maximum eigenvalue, and $\alpha$ is the power law exponent that

MAKE THIS MORE CLEAR
CLARIFY HOW CONV2D lsyers are treated

>>>>

Let us write the Energy Landscape (or optimization function) for a typical DNN with $L$ layers as
\begin{equation}
E_{DNN}=h_{L}(\mathbf{W}_{L}\times h_{L-1}(\mathbf{W}_{L-1}\times h_{L-2}(\cdots)+\mathbf{b}_{L-1})+\mathbf{b}_{L})  .
\label{eqn:dnn_energy}
\end{equation}

with activation functions $h_{l}(\cdot)$,  weight matrices $\mathbf{W}_{l}$, and the biases $\mathbf{b}_{l}$.

The model has been (or will be) trained on (unspecified) labeled data $\{d_{i},y_{i}\}\in\mathcal{D}$, 
using Backprop, by minimizing some (also unspecified) loss function $\mathcal{L}()$.  Moreover, we expect that most well trained,. production quality models will employ 1 or more forms of on regularization, such as Batch Normalization, Dropout, etc, and will also contain additional structure such as Skip Connections etc. Here, we ignore these details, and focus only on the weight matrices.

Each layer contains by one or more layer 2D weight matrices $\mathbf{W}_{L}$, and/or the 2D feature maps $\mathbf{W}_{i,L}$ extracted from 2D Convolutional layers.  (For notational convenience, we may drop the $i$ and/or $i,l$ subscripts below.) We assume the layer weight matrices are statistically independent, allowing us to estimate the Complexity, or test accuracy, with a standard Product Norm, which resembles a data dependent VC complexity

\begin{equation}
\mathcal{C}\sim\Vert\mathbf{W}_{1}\Vert\times\Vert\mathbf{W}_{2}\Vert\cdots\Vert\mathbf{W}_{L}\Vert ,
\end{equation}
where $\mathbf{W}$ is an $(N\times M)$ weight matrix, with $N\ge M$, and 
 $\Vert\mathbf{W}\Vert$ is some matrix Norm, such as the:

\begin{itemize}
 \item Frobenius Norm: $\Vert\mathbf{W}\Vert^{2}_{F}=\Vert\mathbf{W}\Vert^{2}_{2}=\sum_{i,j}w^{2}_{i,j}$,
 \item Spectral Norm:  $\Vert\mathbf{W}\Vert_{\infty}=\lambda_{max}$, or even the
 \item $\alpha$-Norm (or Shatten Norm) $\Vert\mathbf{W}\Vert^{\alpha}_{\alpha}=\sum_{i=1}^{M}\lambda^{\alpha}$,
\end{itemize}

where $\lambda_{i}$ is the $i-th$ eigenvalue of the correlation matrix $\mathbf{X}=\dfrac{1}{N}\mathbf{W}^{T}\mathbf{W}$, and $\lambda_{max}$ is the maximum eigenvalue.

The exponent $\alpha$ is the power law exponent that arise in our \emph{Theory of Heavy Tailed Self Regularization}, and is the determined by fitting the Empirical Spectral Density (ESD) of $\mathbf{X}$--i.e. a histogram of the eigenvalues--$\rho(\lambda)$ to a truncated power law

\begin{equation}
\rho(\lambda)\sim\lambda^{\alpha},\;\;\lambda\le\lambda_{max}
\end{equation}

---

CLARIFY HOW CONV2D lsyers are treated

----
